Hydras and Cie \\ Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq

### 2021-09-24 doc/JFLA2022/paper.tex
Minor \cite fixes.

\subsection{Vision}
The \emph{Hydra-battles} project, part of \emph{Coq-Community}~\cite{CoqCommunity} aims to be an experimental platform for the collaborative development of commented libraries of formal proofs. \emph{Coq-Community} is a community organization that we have founded in 2018 with two goals in mind: providing a solution for the long-term maintenance of interesting Coq packages, and working collaboratively on documentation projects. The \emph{Hydra-battles} project demonstrates that these two goals are not independent: interesting Coq packages can become the basis for new documentation.
%
This umbrella project now includes evolved versions of former \emph{contribs} Cantor and Additions (under the new names of Hydra-battles and Addition-chains), the Pocklington library, extracted from Russel O'Connor's Goedel \emph{contrib}\cite{OConnor05, Goedel} and a bridge to the Gaia library (\emph{contrib} of José Grimm~\cite{Gaia,grimm:hal-00911710}).
%
By following this approach of commenting interesting Coq packages, we provide new documentation content, that contributes to the diversity of the thriving Coq documentation ecosystem.

@@

\TODO[Clément]{Is there a word missing above?}
Considering measures applicable to \emph{all} battles allowed us to
focus on battles where the hydra can make an arbitrary number of copies at any time, which made our proof by contradiction artificially easier.
Unfortunately, the examples  most commonly shown in the litterature
(see for instance \cite{KP82, bauer2008, BauerHydra}) 
assume that the hydra grows $n$ copies at step $n$ of the game, which is incompatible with our proof.

@@

In order to prove formally that the length of the considered
kind of battles is not given by a primitive recursive function, we used the formalization of primitive recursive functions, part
of Russell O'Connor's contribution on G\"{o}del first incompleteness theorem \cite{OConnor05, Goedel}.
For this purpose, and above all by consideration of the scientific interest of this contribution, we chose to host and maintain this work within \textit{Coq-Community}.

>>>>

\subsection{Vision}
The \emph{Hydra-battles} project, part of \emph{Coq-Community}~\cite{CoqCommunity} aims to be an experimental platform for the collaborative development of commented libraries of formal proofs. \emph{Coq-Community} is a community organization that we have founded in 2018 with two goals in mind: providing a solution for the long-term maintenance of interesting Coq packages, and working collaboratively on documentation projects. The \emph{Hydra-battles} project demonstrates that these two goals are not independent: interesting Coq packages can become the basis for new documentation.
%
This umbrella project now includes evolved versions of former \emph{contribs} Cantor and Additions (under the new names of Hydra-battles and Addition-chains), the Pocklington library, extracted from Russel O'Connor's Goedel \emph{contrib}~\cite{OConnor05, Goedel} and a bridge to the Gaia library (\emph{contrib} of José Grimm~\cite{Gaia,grimm:hal-00911710}).
%
By following this approach of commenting interesting Coq packages, we provide new documentation content, that contributes to the diversity of the thriving Coq documentation ecosystem.

@@

\TODO[Clément]{Is there a word missing above?}
Considering measures applicable to \emph{all} battles allowed us to
focus on battles where the hydra can make an arbitrary number of copies at any time, which made our proof by contradiction artificially easier.
Unfortunately, the examples  most commonly shown in the litterature
(see for instance~\cite{KP82, bauer2008, BauerHydra}) 
assume that the hydra grows $n$ copies at step $n$ of the game, which is incompatible with our proof.

@@

In order to prove formally that the length of the considered
kind of battles is not given by a primitive recursive function, we used the formalization of primitive recursive functions, part
of Russell O'Connor's contribution on G\"{o}del first incompleteness theorem~\cite{OConnor05, Goedel}.
For this purpose, and above all by consideration of the scientific interest of this contribution, we chose to host and maintain this work within \textit{Coq-Community}.
